PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-06-27 paper/ms.tex
minor proof correction

We wish \ptfob\ were a planet. It would be quite exceptional. It would be the
youngest known \added{transiting\footnote{Younger hot Jupiters have been
reported around V830 Tau, TAP 26, and CI Tau
\citep{johns-krull_CI_Tau_candidate_2016,donati_hot_2016,donati_hot_2017,yu_hot_2017,flagg_co_2019}.}}
hot Jupiter \citep{van_eyken_ptf_2012}, orbiting a T Tauri star in the
Orion-OB1a cluster.  It would have the shortest orbital period of any hot
Jupiter.  With such a short period, it would probably be filling its Roche
lobe, and actively losing mass to its host star.  Not only that, but the
rapidly-rotating host star is probably oblate enough to \replaced{torque the
planet's orbit into and out of the transiting configuration}{cause the planet's
orbit to precess into and out of the transiting configuration} on a timescale
of years
\citep{barnes_measurement_2013,ciardi_followup_2015,kamiaka_revisiting_2015}.

>>>>

We wish \ptfob\ were a planet. It would be quite exceptional. It would be the
youngest known \added{transiting\footnote{Younger hot Jupiters have been
reported around V830 Tau, TAP 26, and CI Tau
\citep{johns-krull_CI_Tau_candidate_2016,donati_hot_2016,donati_hot_2017,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.}}
hot Jupiter \citep{van_eyken_ptf_2012}, orbiting a T Tauri star in the
Orion-OB1a cluster.  It would have the shortest orbital period of any hot
Jupiter.  With such a short period, it would probably be filling its Roche
lobe, and actively losing mass to its host star.  Not only that, but the
rapidly-rotating host star is probably oblate enough to \replaced{torque the
planet's orbit into and out of the transiting configuration}{cause the planet's
orbit to precess into and out of the transiting configuration} on a timescale
of years
\citep{barnes_measurement_2013,ciardi_followup_2015,kamiaka_revisiting_2015}.
